---
title: "Simple document"
output: html_document
---
```{r, message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
`r round(mean(samp),2)` #this will round to 2 decimal places

# Section 3

## Plot from last time

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.
(Option command i to make code chunk)

```{r, chunk_scatterplot, echo=FALSE}
plot_df=
  tibble(
    x=rnorm(n=1000),
    y=1 + 2 * x + rnorm(n=1000)
  )
ggplot(plot_df, aes(x=x,y=y)) + geom_point()
```
```{r chunk_histogram}
ggplot(plot_df,aes(x=x)) + geom_histogram()
```

### Plot for learning assessment

```{r, chunk_assessment}
assessment_df=
  tibble(
    num_var=rnorm(n=500, mean=1),
    num_var_pos=num_var >0,
    abs_num_var=abs(num_var)
  )
ggplot(assessment_df,aes(x=abs_num_var)) + geom_histogram()
```

Here's a list:
* List item 1
* List item 2